More than one Author with different Affiliations

### 2016-04-12 NatPlant2/manuscript.tex
updates

\subsection*{Hard sweeps do not shape genome-wide diversity in maize} %JRI
Our findings demonstrate that classic hard selective sweeps have not contributed substantially to genome-wide patterns of diversity in maize, a result we show is robust to concerns about power due to the effects of purifying selection  \cite{enard2014}. 
Although our approach ignores the potential for hard sweeps in noncoding regions of the genome, a growing body of evidence argues against hard sweeps as the prevalent mode of selection shaping maize variability. 
Among well-characterized domestication loci, only the gene \emph{tga1} shows evidence of a hard sweep on a missense mutation \cite{wang2015}, while published data for several loci are consistent with soft sweeps from standing variation \cite{studer2011} or multiple mutations \cite{wills2013}. 
Moreover, genome-wide studies of domestication \cite{hufford2012},  local adaptation \cite{Takuno15062015} and modern breeding \cite{van2012historical, beissinger2014} all support the importance of standing variation as primary sources of adaptive variation. 
Soft sweeps are expected to be common when $2N_e\mu_b \ge 1$, where $\mu_b$ is the mutation rate of beneficial alleles with selection coefficient $s_b$ \cite{messer2013}. Assuming a mutation rate of $3 \times 10^{-8}$ \cite{clark2005} and that on the order of $\approx 1-5\%$ of mutations are beneficial \cite{eyre2007}, this implies that soft sweeps should be common in both maize and teosinte for mutational targets $>>10kb$ --- a plausible size for quantitative traits or for regulatory evolution targeting genes with large up- or down-stream control regions \cite[e.g.]{studer2011}.
Indeed, many adaptive traits in both maize \cite{wallace2014} and teosinte \cite{weber2008} are highly quantitative,  and adaptation in both maize \cite{hufford2012} and teosinte \cite{pyhajarvi2013} has involved selection on regulatory variation.

>>>>

\subsection*{Hard sweeps do not shape genome-wide diversity in maize} %JRI
Our findings demonstrate that classic hard selective sweeps have not contributed substantially to genome-wide patterns of diversity in maize, a result we show is robust to concerns about power due to the effects of purifying selection  \cite{enard2014}. 
Although our approach ignores the potential for hard sweeps in noncoding regions of the genome, a growing body of evidence argues against hard sweeps as the prevalent mode of selection shaping maize variability. 
Among well-characterized domestication loci, only the gene \emph{tga1} shows evidence of a hard sweep on a missense mutation \cite{wang2015}, while published data for several loci are consistent with soft sweeps from standing variation \cite{studer2011} or multiple mutations \cite{wills2013}. 
Moreover, genome-wide studies of domestication \cite{hufford2012},  local adaptation \cite{Takuno15062015} and modern breeding \cite{van2012historical, beissinger2014,hirsch2014} all support the importance of standing variation as primary sources of adaptive variation. 
Soft sweeps are expected to be common when $2N_e\mu_b \ge 1$, where $\mu_b$ is the mutation rate of beneficial alleles with selection coefficient $s_b$ \cite{messer2013}. Assuming a mutation rate of $3 \times 10^{-8}$ \cite{clark2005} and that on the order of $\approx 1-5\%$ of mutations are beneficial \cite{eyre2007}, this implies that soft sweeps should be common in both maize and teosinte for mutational targets $>>10kb$ --- a plausible size for quantitative traits or for regulatory evolution targeting genes with large up- or down-stream control regions \cite[e.g.]{studer2011}.
Indeed, many adaptive traits in both maize \cite{wallace2014} and teosinte \cite{weber2008} are highly quantitative,  and adaptation in both maize \cite{hufford2012} and teosinte \cite{pyhajarvi2013} has involved selection on regulatory variation.
